### 2021-01-25 introduction.tex
first introduction fit

A previous work has argued in favor of dynamic analysis for mining sandboxes, instead of using static analysis \cite{jamrozik2016mining}. The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes domain. However, they do not provide any empirical validation about this claim, and there was no effective discussion about the possibility of combination of both proposals. Moreover, Bao et al. \cite{bao2018mining} present an empirical study comparing different dynamic analysis tools for mining sandboxes, that leverage DroidFax \cite{cai2017droidfax} to instrument 102 pairs of Android apps (each pair comparing a benign and a malign version of an App), and collect information needed to mine sandboxes. Although the authors report an efficient in identifying 70\% of the malware in this specific dataset, part of this result is due to an internal static analysis algorithm of DroidFax, which might improve the performance of the dynamic analysis tools for mining sandboxes, introducing a possible threat to the work.

>>>>

A previous work has argued in favor of dynamic analysis for mining sandboxes, instead of using static analysis \cite{jamrozik2016mining}. The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes domain because the analysis must often assume that more behaviors are possible than actually would be, and if static analysis determine that some behavior is impossible, this behavior no longer needs to be checked at runtime. Thereby, code that is interpreted, decrypted, or downloaded at run time is challenging for static analysis. However, they do not provide any empirical validation about this claim, and there was no effective discussion about the possibility of combination of both proposals. Moreover, Bao et al. \cite{bao2018mining} present an empirical study comparing different dynamic analysis tools for mining sandboxes, that leverage DroidFax \cite{cai2017droidfax} to instrument 102 pairs of Android apps (each pair comparing a benign and a malign version of an App), and collect information needed to mine sandboxes. Although the authors report an efficient in identifying 70\% of the malware in this specific dataset, part of this result is due to an internal static analysis algorithm of DroidFax, which might improve the performance of the dynamic analysis tools for mining sandboxes, introducing a possible threat to the work.
